---
title: "Alcohol vs Seat choice"
author: "Carolina Alameda"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??
## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

Visually the plot shows a large difference between the back row and the middle row. The plot shows an even larger difference the back and front row.  

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
  
 According to the chart the back row drink 8.5 more drinks than the middle row, which they drink 3.3 drinks per week, and the front row drinks 1.7 per week. It is reasonable to assume that they are not drinking the same amount.  
  
## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The P value represents the chances of getting a result like we just obtained if the null hypothesis is actually true. Since the result is so small, I am going to reject the null hypothesis.  
We know need to try and discover what is different from the other.  
```{r}
plot(TukeyHSD(model1))
```

According to this chart, the middle and front do not have a difference, however the front-back and the back-middle are different.  

## Conclusions


